Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-13 eswc-2012/phdsymp.tex
snip
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@88 43ef1190-90fd-4dd7-a769-d0121f02b80e

The contemporary problem in benchmarking is to distinguish
implementations when the measured difference is small or susceptible
to random noise.

@@

In this case, we must consider the possibility that the measurements
are impacted by random noise. For example: The underlying system may
be doing other tasks. The garbage collection of some languages may
trigger at not easily foreseeable points. The engine may use
randomized algorithms, or the data may be of such a nature that it
triggers worst-case behaviour in situations the query writer cannot
foresee. All this contributes to that we should consider the
performance metric, whatever metric is used, as a \emph{stochastic
  variable}.

>>>>

@@

In this case, we must consider the possibility that the measurements
are impacted by random noise. Sources of random noise may be the
overall system load, garbage collection triggers, use of randomized
algorithms, or the data of such a nature that it triggers worst-case
behaviour, etc. All this contributes to that we should consider the
performance metric, whatever metric is used, as a \emph{stochastic
  variable}.
